Dependent Object Types

### 2012-09-13 doc/fool/article.tex
extra and, but nothing missing
fixing and reducing claim of list example -- remove it?

\subsection{Polymorphic Lists}
Polymorphic lists can be expressed using an abstract type member for
the element type ($\mi{Elem}$). We can instantiate a refinement of the
list package to manipulate lists with a particular element type. We
can choose to make the lists invariant or covariant in the element
type by fixing the lower bound of the $\mi{Elem}$ re-declaration to
the upper bound or to $\Bot$, respectively.
\begin{align*}
&\mlnew {\mi{genLists}} {\Top \mlrefine g {\Ldecl {\mi{ListPackage}} \Bot {\Top \mlrefine p {\\\displaybreak[3]
&\ \Ldecl {\mi{Elem}} \Bot \Top\\\displaybreak[3]
&\ \Ldecl {\mi{ListOfElement}} {g.\mi{List} \refine z {\Ldecl {\mi{Elem}} {p.\mi{Elem}} {p.\mi{Elem}}}} {\\&\gap\gap\gap\gap g.\mi{List} \refine z {\Ldecl {\mi{Elem}} {p.\mi{Elem}} {p.\mi{Elem}}}}\\\displaybreak[3]
&\ \Ldecl {\mi{List}} \Bot {\Top \mlrefine z {\\\displaybreak[3]
&\ \gap \mdecl {\mi{isEmpty}} {\mi{root}.\mi{Unit}} {\mi{root}.\mi{Boolean}}\\\displaybreak[3]
&\ \gap \mdecl {\mi{head}} {\mi{root}.\mi{Unit}} {g.\mi{Elem}}\\\displaybreak[3]
&\ \gap \mdecl {\mi{tail}} {\mi{root}.\mi{Unit}} {g.\mi{ListOfElem}}\\\displaybreak[3]
&\gap}}\\\displaybreak[3]
&\ \mdecl {\mi{nil}} {\mi{root}.\mi{Unit}} {g.\mi{ListOfElem}}\\\displaybreak[3]
&\ \mdecl {\mi{cons}} {g.\mi{Elem}} {g.\mi{ListOfElem}}\\\displaybreak[3]
&}}}}{
\mlnew {\mi{natLists}} {{\mi{genLists}.\mi{ListPackage}} \mlrefine p {\\\displaybreak[3]
&\gap \Ldecl {\mi{Elem}} {\mi{root}.\mi{Nat}} {\mi{root}.\mi{Nat}} }\mlldefs{\\\displaybreak[3]
&\ {\mi{nil}}(u) = \ldots\\\displaybreak[3]
&\ {\mi{cons}}(u) = \ldots\\\displaybreak[3]
&}}}{
\ldots
}
\end{align*}

@@

\subsubsection{Completing the environment to agree with the store}
$\relg k s \Gamma$ defines a singleton set of a completed environment
that agrees with a store $s$ by simply copying the constructor type
from the store for each missing variable.
\begin{align*}
&\relg k s \Gamma = \{ \Gamma, \seq{x_i : T_{c_i}}^{m \leq i < n} \ |\\
&\gap \Gamma = \seq{x : T}^m \andl s = \seq{x \mapsto c}^n \andl\\
&\}
\end{align*}

>>>>

\subsection{Lists}
Polymorphic lists can be expressed using an abstract type member for
the element type ($\mi{Elem}$). We can instantiate a refinement of the
list package to manipulate lists with a particular element type.
\begin{align*}
&\mlnew {\mi{genLists}} {\Top \mlrefine g {\Ldecl {\mi{ListPackage}} \Bot {\Top \mlrefine p {\\\displaybreak[3]
&\ \Ldecl {\mi{Elem}} \Bot \Top\\\displaybreak[3]
&\ \Ldecl {\mi{List}} \Bot {\Top \mlrefine z {\\\displaybreak[3]
&\ \gap \mdecl {\mi{isEmpty}} {\mi{root}.\mi{Unit}} {\mi{root}.\mi{Boolean}}\\\displaybreak[3]
&\ \gap \mdecl {\mi{head}} {\mi{root}.\mi{Unit}} {p.\mi{Elem}}\\\displaybreak[3]
&\ \gap \mdecl {\mi{tail}} {\mi{root}.\mi{Unit}} {p.\mi{List}}\\\displaybreak[3]
&\gap}}\\\displaybreak[3]
&\ \mdecl {\mi{nil}} {\mi{root}.\mi{Unit}} {p.\mi{List}}\\\displaybreak[3]
&\ \mdecl {\mi{cons}} {p.\mi{Elem}} {\arrow {p.\mi{List}} {p.\mi{List}}}\\\displaybreak[3]
&}}}}{
\mlnew {\mi{natLists}} {{\mi{genLists}.\mi{ListPackage}} \mlrefine p {\\\displaybreak[3]
&\gap \Ldecl {\mi{Elem}} {\mi{root}.\mi{Nat}} {\mi{root}.\mi{Nat}} }\mlldefs{\\\displaybreak[3]
&\ {\mi{nil}}(u) = \ldots\\\displaybreak[3]
&\ {\mi{cons}}(hd) = \ldots\\\displaybreak[3]
&}}}{
\ldots
}
\end{align*}

@@

\subsubsection{Completing the environment to agree with the store}
$\relg k s \Gamma$ defines a singleton set of a completed environment
that agrees with a store $s$ by simply copying the constructor type
from the store for each missing variable.
\begin{align*}
&\relg k s \Gamma = \{ \Gamma, \seq{x_i : T_{c_i}}^{m \leq i < n} \ |\\
&\gap \Gamma = \seq{x : T}^m \andl s = \seq{x \mapsto c}^n\\
&\}
\end{align*}
